---
title: "anatomy_of_a_description"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{anatomy_of_a_description}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rhelpi18n)
```

At the time of translation module creation, the handy package function `i18n_module_create()` 
initialize a minimal DESCRIPTION file in the new module. Let's share some advices and best practice for 
filling up the values in here.

Let's start with the translation module of ggplot2 into `language = "fr"`

## Package, Translates and Version

Package is set-up by the `i18n_module_create()` to be the translation
module name.
Translates gets the package name and version :  

We recommend translation module **version** to match the **package version**.

``` yaml
Package: ggplot2
Version: 3.5.1
```
becomes

``` yaml
Package: ggplot2.fr
Version: 3.5.1
Type: Translation-module
Translates: ggplot2 (== 3.5.1)
```


## Title and Description

Both shall be the exact translation of the original Title and Description.


``` yaml
Title: Create Elegant Data Visualisations Using the Grammar of Graphics
Description: A system for 'declaratively' creating graphics,
    based on "The Grammar of Graphics". You provide the data, tell 'ggplot2'
    how to map variables to aesthetics, what graphical primitives to use,
    and it takes care of the details.
```

turns into

``` yaml
Title: Crée des Visualisations de Données Élégantes Basées sur la Grammaire des Graphiques
Description: Un système pour créer des graphiques de manière 'déclarative', basé sur
    "The Grammar of Graphics". Vous fournissez les données, vous indiquez à 'ggplot2'
    la correspondance des variables avec les paramêtres esthétiques, la primitive graphique 
    à utiliser, et 'ggplot2' s'occupe de tous les détails.
```

## Type, Language and Encoding

 Type and Language are set by the `i18n_module_create()` function to be `Translation-module` and
 the configured "language" value.  
 Encoding must be `UTF-8`
 
``` yaml
Type: Translation-module
Encoding: UTF-8
Language: fr
```

## imports and Remotes

For the time beeing, {rhelpi18n} is only available in github and is a prerequisite for your 
translation module. We can use DESCRIPTION to manage both : 

``` yaml
imports:
    rhelpi18n
Remotes: 
    eliocamp/rhelpi18n
```

## Authors, Licence, BugReports

All shall be filled as usual with the module author and module URL.


 

